---
title: "demographic data preprocessing in A-FFIP (BOSCA battery)"
author: "Nico Bast"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: cerulean
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

- purpose: create one dataframe "demogr" that contains one measurement timepoint per row
- info: combines data of two databases (RCT = ASD, nonASD, nonASD follow-up; FU = ASD follow-up)
- info: timepoint FU4 is not considered now as too few cases

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

#required packages
require(dplyr)
require(RColorBrewer)
require(ggplot2)
require(kableExtra)
require(gridExtra)
require(readxl)

#set theme
theme_set(theme_bw())

#data_path
datapath<-'C:/Users/nico/PowerFolders/data_AFFIP/database_exports/2024_03/' 

savepath<-'C:/Users/nico/PowerFolders/data_AFFIP/'
eyetracking_dataquality_file<-"C:/Users/nico/PowerFolders/data_AFFIP/data/Quality sheet/AFFIPeyetracking_quality.xlsx"

rctstatus_path<-"C:/Users/nico/PowerFolders/data_AFFIP/rct_data/export_random_20230728.csv"

```

# load RCT data (clincial trial group)

- received therapy as defined in the A-FFIP RCT trial

```{r}

rct_status<-read.csv(rctstatus_path)
rct_status<-rct_status[rct_status$centno==1,names(rct_status) %in% c('scrnno','rndm')]

rct_status$rndm<-as.factor(rct_status$rndm)
levels(rct_status$rndm)<-c('A-FFIP','EIAU')

rct_status$scrnno<-as.character(rct_status$scrnno)
rct_status$scrnno<-ifelse(nchar(rct_status$scrnno)==2,paste0('0',rct_status$scrnno),rct_status$scrnno)
rct_status$scrnno<-ifelse(nchar(rct_status$scrnno)==1,paste0('00',rct_status$scrnno),rct_status$scrnno)

```


# load checklist 

- as master merge file (March 2024 - all included)

```{r prepare database output}

list.files(datapath)

##LOAD checklist####
checklist_rct<-read_xlsx(paste0(datapath,'RCT/Checkliste.xlsx'))
checklist_fu<-read_xlsx(paste0(datapath,'FU/Checkliste.xlsx'))

#correct wrong entry of ID_Bado in FU database
wrong_entry<-checklist_fu$ID_Bado[!checklist_fu$ID_Bado %in% checklist_rct$ID_Bado]
checklist_fu$ID_Bado[checklist_fu$ID_Bado==wrong_entry]<-"14854-2018"

checklist_rct <- select(checklist_rct, ID_Bado, ID_Studie, Geschlecht_Index, Geburt_Index, Gruppe)
checklist_fu <- select(checklist_fu, ID_Bado, ID_Studie, Geschlecht_Index, Geburt_Index, Gruppe)

print('demographic data is available for:')
checklist_rct$ID_Studie

```

# IQ data

- calculate based on WPPSI or Bayley measures
- IQ is either value measure by Bayley, WPPSI (3rd or 4th edition), and WISC (specific to follow-up)

```{r derive IQ}

##LOAD Bayley/WPPSI####
#WPPSI:
wppsi3 <- read_xlsx(paste0(datapath,'RCT/WPPSI_3_0_3_11.xlsx'))
wppsi3 <- select(wppsi3, ID_Bado, Datum, Messzeitpunkt, Verbalteil_IQ, Handlungsteil_IQ)
wppsi3$test <- "wppsi3"
names(wppsi3)<-c('ID_Bado','date_iq','t','verbal_iq','nonverbal_iq','iq_test')


wppsi4_rct <- read_xlsx(paste0(datapath,'RCT/WPPSI_4_0_7_2.xlsx'))
wppsi4_fu <- read_xlsx(paste0(datapath,'FU/WPPSI_4_0_7_2.xlsx'))
wppsi4_rct <- select(wppsi4_rct, ID_Bado, Datum, Messzeitpunkt, Verbalteil_IQ, Handlungsteil_IQ)
wppsi4_fu <- select(wppsi4_rct, ID_Bado, Datum, Messzeitpunkt, Verbalteil_IQ, Handlungsteil_IQ)
wppsi4<-rbind(wppsi4_rct,wppsi4_fu)
wppsi4$test <- "wppsi4"
names(wppsi4)<-c('ID_Bado','date_iq','t','verbal_iq','nonverbal_iq','iq_test')

wisc4_RCT <- read_xlsx(paste0(datapath,'RCT/HAWIK-IV.xlsx'))
wisc4_FU <- read_xlsx(paste0(datapath,'FU/WISC_IV.xlsx'))
wisc4_RCT <- select(wisc4_RCT, ID_Bado, DatumHawikIV, Meßzeit_HawikIV, Hawik_IV_SV, Hawik_IV_WLD )
wisc4_FU <- select(wisc4_FU, ID_Bado, DatumWISC, Meßzeit_WISC, WISC_WLD_IQ_tab)
names(wisc4_RCT)<-c('ID_Bado','date_iq','t','nonverbal_iq','verbal_iq','nonverbal_iq')
names(wisc4_FU)<-c('ID_Bado','date_iq','t','nonverbal_iq','nonverbal_iq')
wisc4_FU$verbal_iq<-NA
wisc4_FU$iq_test<-"wisc4"
wisc4_RCT$iq_test<-"wisc4"
wisc4<-rbind(wisc4_RCT,wisc4_FU)

wppsi <- rbind(wppsi3, wppsi4, wisc4)


#BAYLEY:
bayley_rct <- read_xlsx(paste0(datapath,'RCT/Bayley III.xlsx'))
bayley_fu <- read_xlsx(paste0(datapath,'FU/Bayley III.xlsx'))

bayley_rct <- select(bayley_rct, ID_Bado, Datum_BayleyIII, Meßzeit_BayleyIII, SprR_EQ, Kog_EQ)
bayley_fu <- select(bayley_fu, ID_Bado, Datum_BayleyIII, Meßzeit_BayleyIII, SprR_EQ, Kog_EQ)

bayley<-rbind(bayley_rct,bayley_fu)

names(bayley) <- c("ID_Bado",'date_iq',"t","verbal_iq", "nonverbal_iq")
bayley$iq_test<-'bayley3'

#get one data frame for cognitive ability
cog_abil <- rbind(bayley, wppsi)

#number of unique iq estimates
length(unique(interaction(cog_abil$ID_Bado,cog_abil$t)))

```

- remove duplicates and recover incomplete entries in IQ data

```{r}
# #check if there are duplicates (probably wppsi cognitive and bayley sprache eingegeben)
duplicates<-interaction(cog_abil$ID_Bado,cog_abil$t)[duplicated(interaction(cog_abil$ID_Bado,cog_abil$t))] 
cog_abil_no_duplicates<-cog_abil[!(interaction(cog_abil$ID_Bado,cog_abil$t) %in% duplicates),]

#remove double entries:
cog_abil_duplicates<-cog_abil[interaction(cog_abil$ID_Bado,cog_abil$t) %in% duplicates,]
cog_abil_duplicates<-unique(cog_abil_duplicates) 

#differentiate to  complete and incomplete duplicates:
cog_abil_complete_duplicates<-cog_abil_duplicates[!is.na(cog_abil_duplicates$verbal_iq) &
                                                    !is.na(cog_abil_duplicates$nonverbal_iq),]
cog_abil_incomplete_duplicates<-cog_abil_duplicates[is.na(cog_abil_duplicates$verbal_iq) |
                                                    is.na(cog_abil_duplicates$nonverbal_iq),]

#select incomplete duplicates that can be recovered as they have two entries:
duplicates_incomplete<-interaction(cog_abil_incomplete_duplicates$ID_Bado,
                            cog_abil_incomplete_duplicates$t)[
                            duplicated(interaction(cog_abil_incomplete_duplicates$ID_Bado,
                                                   cog_abil_incomplete_duplicates$t))] 

cog_abil_incomplete_duplicates_nonrecover<-cog_abil_incomplete_duplicates[
  !(interaction(cog_abil_incomplete_duplicates$ID_Bado,cog_abil_incomplete_duplicates$t) %in% duplicates_incomplete),]

cog_abil_incomplete_duplicates_recover<-cog_abil_incomplete_duplicates[
  (interaction(cog_abil_incomplete_duplicates$ID_Bado,cog_abil_incomplete_duplicates$t) %in% duplicates_incomplete),]

#recoverable incomplete duplicates: order by id and timepoint
cog_abil_incomplete_duplicates_recover<-cog_abil_incomplete_duplicates_recover[
  order(cog_abil_incomplete_duplicates_recover$ID_Bado,cog_abil_incomplete_duplicates_recover$t),]

#recoverable incomplete duplicates: to odd and even set that can be merged 
cog_abil_incomplete_duplicates_recover_odd<-cog_abil_incomplete_duplicates_recover[seq(1,46,2),]
cog_abil_incomplete_duplicates_recover_even<-cog_abil_incomplete_duplicates_recover[seq(2,46,2),]
cog_abil_incomplete_duplicates_recover_even<-select(cog_abil_incomplete_duplicates_recover_even,
                                                    ID_Bado,t,verbal_iq,nonverbal_iq)
cog_abil_incomplete_duplicates_recover<-merge(cog_abil_incomplete_duplicates_recover_odd,
                                              cog_abil_incomplete_duplicates_recover_even,
                                              by=c('ID_Bado','t'))

#recoverable incomplete duplicates: recover process
cog_abil_incomplete_duplicates_recover$verbal_iq.x<-
     with(cog_abil_incomplete_duplicates_recover,ifelse(is.na(verbal_iq.x),verbal_iq.y,verbal_iq.x))

cog_abil_incomplete_duplicates_recover$nonverbal_iq.x<-
     with(cog_abil_incomplete_duplicates_recover,ifelse(is.na(nonverbal_iq.x),nonverbal_iq.y,nonverbal_iq.x))

cog_abil_incomplete_duplicates_recover<-select(cog_abil_incomplete_duplicates_recover,
                                               ID_Bado,t,date_iq,verbal_iq.x,nonverbal_iq.x,iq_test)

names(cog_abil_incomplete_duplicates_recover)<-c('ID_Bado','t','date_iq','verbal_iq','nonverbal_iq','iq_test')


#bind all together: no duplicate , complete duplicates, nonrecover duplicates, recovered duplicates (recover)
cog_abil<-rbind(
  cog_abil_no_duplicates,
  cog_abil_complete_duplicates,
  cog_abil_incomplete_duplicates_nonrecover,
  cog_abil_incomplete_duplicates_recover
)

##avaialable data

with(cog_abil,table(t,!is.na(nonverbal_iq)))
with(cog_abil,table(iq_test))

#number of unique iq estimates
length(unique(interaction(cog_abil$ID_Bado,cog_abil$t)))

```

# load ADI

```{r load measures}

##LOAD ADI####
ADI <- read_xlsx(paste0(datapath,'RCT/ADI-R.xlsx'))
ADI$adi.sum.algo <- ADI$ADI_alg_SOZ_INT+ADI$ADI_alg_KOM+ADI$ADI_alg_RITUALE
ADI$adi.sum.toddler <- ADI$ADI_Toddler_ges
ADI$adi.sum.algo[ADI$adi.sum.toddler>1]<-NA
ADI <- select(ADI, ID_Bado, DatumADI, adi.sum.algo, adi.sum.toddler)
names(ADI)[names(ADI)=='DatumADI']<-'date_adi'

##remove duplicated value (ADI difference by one point)
ADI$ID_Bado[duplicated(ADI$ID_Bado)]
ADI<-ADI[!duplicated(ADI$ID_Bado),]

hist(ADI$adi.sum.algo)
hist(ADI$adi.sum.toddler)

```


# load ADOS data 

- combine data of different modules
- ADOS is only available in RCT data, not for FU

```{r ados}

##LOAD ADOS####
ADOS_M1 <- read_xlsx(paste0(datapath,'RCT/ADOS_2_M1_G_WPS.xlsx'))
ADOS_M1 <- ADOS_M1[!ADOS_M1$rating!=1,] #exclude video coding - removes duplicates
ADOS_M1 <- select(ADOS_M1, ID_Bado, DatumADOS_2_M1_G_WPS,Severity_SA, Severity_RRB, Severity_Gesamt)
names(ADOS_M1)[names(ADOS_M1)=="DatumADOS_2_M1_G_WPS"]<-'date_ados'
ADOS_M1$module <- "1"

ADOS_M2 <- read_xlsx(paste0(datapath,'RCT/ADOS_2_M2_WPS.xlsx'))
ADOS_M2 <- ADOS_M2[!ADOS_M2$rating!=1,] #exclude video coding
ADOS_M2 <- select(ADOS_M2, ID_Bado, DatumADOS_2_M2,Severity_SA, Severity_RRB, Severity_Gesamt)
names(ADOS_M2)[names(ADOS_M2)=="DatumADOS_2_M2"]<-'date_ados'
ADOS_M2$module <- "2"
ADOS <- rbind(ADOS_M1, ADOS_M2)

hist(ADOS$Severity_Gesamt)

```

# load BOSCC

```{r BOSCC}

####LOAD BOSCC###
BOSCC <- read_xlsx(paste0(datapath,'RCT/BOSCC.xlsx')) # only available for RCT
BOSCC <- select(BOSCC, ID_Bado, Meßzeit_BOSCC, Datum_BOSCC,BOSCC_Average_Total, BOSCC_SA, BOSCC_RRB)
names(BOSCC)<-c('ID_Bado','t','date_boscc','BOSCC_Average_Total','BOSCC_SA','BOSCC_RRB')

hist(BOSCC$BOSCC_Average_Total)
with(BOSCC,table(t,!is.na(BOSCC_Average_Total)))

```

# load ESCS

```{r ESCS}

ESCS <- read_xlsx(paste0(datapath,'RCT/ESCS.xlsx'))
ESCS <- select(ESCS,ID_Bado,Meßzeit_ESCS,Datum_ESCS,Total_RJA,Total_IJA,Total_IBR,Total_ISI,Total_RSI)
names(ESCS)[2]<-'t'
names(ESCS)[3]<-'date_escs'

##--> ESCS not available at T6?
with(ESCS,table(is.na(Total_RJA),t))

```

# load CBCL data

```{r CBCL}

####LOAD CBCL###
cbcl_preschool_RCT <- read_xlsx(paste0(datapath,'RCT/CBCL1_5_5.xlsx'))
cbcl_school_RCT <- read_xlsx(paste0(datapath,'RCT/CBCL_4_18.xlsx'))
cbcl_preschool_FU <- read_xlsx(paste0(datapath,'FU/CBCL1_5_5.xlsx'))
cbcl_school_FU <- read_xlsx(paste0(datapath,'FU/CBCL_4_18.xlsx'))

cbcl_preschool_RCT<-select(cbcl_preschool_RCT,ID_Bado, Meßzeit_CBCLV, Datum_CBCLV,
                           CBCLalter, CBCL_T_INT, CBCL_T_EXT, CBCL_T_GES)
cbcl_school_RCT<-select(cbcl_school_RCT,ID_Bado, Meßzeit_CBCL, Datum_CBCL, 
                        CBCLalter, CBCL_T_INT, CBCL_T_EXT, CBCL_T_GES)
cbcl_preschool_FU<-select(cbcl_preschool_FU,ID_Bado, Meßzeit_CBCLV, Datum_CBCLV, 
                          CBCLalter, CBCL_T_INT, CBCL_T_EXT, CBCL_T_GES)
cbcl_school_FU<-select(cbcl_school_FU,ID_Bado, Meßzeit_CBCL, Datum_CBCL,
                       CBCLalter, CBCL_T_INT, CBCL_T_EXT, CBCL_T_GES)

cbcl_preschool_RCT$CBCL_type<-'CBCL1_5'
cbcl_preschool_FU$CBCL_type<-'CBCL1_5'
cbcl_school_RCT$CBCL_type<-'CBCL4_18'
cbcl_school_FU$CBCL_type<-'CBCL4_18'

names(cbcl_preschool_RCT)<-c('ID_Bado','t','date_cbcl','CBCL_age','CBCL_T_INT','CBCL_T_EXT','CBCL_T_GES','CBCL_type')
names(cbcl_preschool_FU)<-c('ID_Bado','t','date_cbcl','CBCL_age','CBCL_T_INT','CBCL_T_EXT','CBCL_T_GES','CBCL_type')
names(cbcl_school_RCT)<-c('ID_Bado','t','date_cbcl','CBCL_age','CBCL_T_INT','CBCL_T_EXT','CBCL_T_GES','CBCL_type')
names(cbcl_school_FU)<-c('ID_Bado','t','date_cbcl','CBCL_age','CBCL_T_INT','CBCL_T_EXT','CBCL_T_GES','CBCL_type')

cbcl<-rbind(
  cbcl_preschool_RCT,
  cbcl_school_RCT,
  cbcl_preschool_FU,
  cbcl_school_FU
)

cbcl<-cbcl[!is.na(cbcl$t),]

hist(cbcl$CBCL_T_GES)
with(cbcl,table(t,!is.na(CBCL_T_GES)))

```

# load SRS

```{r SRS}

####LOAD SRS####
srs_RCT <- read_xlsx(paste0(datapath,'RCT/SRS.xlsx'))
srs_FU <- read_xlsx(paste0(datapath,'FU/SRS.xlsx'))
srs_RCT <- srs_RCT[!srs_RCT$Beurteiler=="Erzieher/innen",]
srs_FU <- srs_FU[!srs_FU$Beurteiler=="Erzieher/innen",]
srs_RCT <- select(srs_RCT, ID_Bado, Meßzeit_SRS, Datum_SRS, Gesamtwert_N_k_RW)
srs_FU <- select(srs_FU, ID_Bado, Meßzeit_SRS, Datum_SRS, Gesamtwert_N_k_RW)
srs<-rbind(srs_RCT,srs_FU)
names(srs)<-c("ID_Bado",'t','date_srs',"srs16_sum")

hist(srs$srs16_sum)
with(srs,table(t,!is.na(srs16_sum)))

```

# load RBS-R

```{r rbsr}

####LOAD RBS-R####
rbs_rct <- read_xlsx(paste0(datapath,'RCT/RBS.xlsx'))
rbs_fu <- read_xlsx(paste0(datapath,'FU/RBS.xlsx'))
rbs_rct <- rbs_rct[!rbs_rct$Beurteiler=="Erzieher/innen",]
rbs_fu <- rbs_fu[!rbs_fu$Beurteiler=="Erzieher/innen",]

rbs_rct <- select(rbs_rct, ID_Bado, Meßzeit_RBS, Datum_RBS, RBSR_ges)
rbs_fu <- select(rbs_fu, ID_Bado, Meßzeit_RBS,  Datum_RBS, RBSR_ges)

rbs<-rbind(rbs_rct,rbs_fu)
names(rbs)[2]<-'t'
names(rbs)[3]<-'date_rbsr'

hist(rbs$RBSR_ges)
with(rbs,table(t,!is.na(RBSR_ges)))

```

# load socioeconomic status 

```{r SES}

SES<-read_xlsx(paste0(datapath,'RCT/SES.xlsx'))
SES <- select(SES,ID_Bado,SES_Schule_Mutter,SES_Beruf_Mutter,SES_Schule_Vater,SES_Beruf_Vater)

```

# remove duplicates

```{r}

ADI<-ADI[!duplicated(ADI$ID_Bado),]
ADOS<-ADOS[!duplicated(ADOS$ID_Bado),]
BOSCC<-BOSCC[!duplicated(interaction(BOSCC$ID_Bado,BOSCC$t)),]
ESCS<-ESCS[!duplicated(interaction(ESCS$ID_Bado,ESCS$t)),]
cbcl<-cbcl[!duplicated(interaction(cbcl$ID_Bado,cbcl$t)),]
srs<-srs[!duplicated(interaction(srs$ID_Bado,srs$t)),]
rbs<-rbs[!duplicated(interaction(rbs$ID_Bado,rbs$t)),] 
SES<-SES[!duplicated(SES$ID_Bado,ESCS$t),]

```

# merge data

- consider that measures are assessed at different timepoints
- however we want a dataframe with one row per timepoint and participant
- this is solved by creating a shadow data frame with all possible timepoints
- controls (K) get no timepoint assigned ---> corrected here

```{r  merge}

#repeat checklist per possible timepoints
checklist_rct$ID_Bado #only use RCT data as all FU are also in RCT
possible_timepoints<-c('T1','T2','T3','T4','T5','T6','FU','FU2','FU3')
ID_Bado<-rep(checklist_rct$ID_Bado,each=length(possible_timepoints))
t<-rep(possible_timepoints,times=nrow(checklist_rct))
shadow_df<-data.frame(ID_Bado,t)

#merge with checklist
demogr<-merge(shadow_df,checklist_rct,by='ID_Bado')

#randomization / group data
demogr<-merge(demogr,rct_status,by.x='ID_Studie',by.y = 'scrnno',all.x=T)

#merge ADOS & ADI & SES - independent of timepoint
demogr<-merge(demogr,ADOS,by='ID_Bado',all.x=T)
demogr <- merge(demogr, ADI, by="ID_Bado", all.x=T)
demogr <- merge(demogr, SES, by="ID_Bado", all.x=T)

#merge BOSCC (t2,t4,t6)
demogr <- merge(demogr, BOSCC, by=c("ID_Bado",'t'), all.x=T)

#merge ESCS (t2,t3,t4,t5)
demogr <- merge(demogr, ESCS, by=c("ID_Bado",'t'), all.x=T)

demogr <- merge(demogr, cbcl, by=c("ID_Bado","t"), all.x=T)
demogr <- merge(demogr, srs, by=c("ID_Bado","t"), all.x=T)
demogr <- merge(demogr, rbs, by=c("ID_Bado","t"), all.x=T)
demogr <- merge(demogr, cog_abil,by=c("ID_Bado","t"),all.x=T)

```

# eye-tracking data quality

load eye tracking data quality and merge to data base entries

```{r prepare eye tracking meta data}

###--> CHECK corresponding ET data ####

et_demogr<-read_xlsx(eyetracking_dataquality_file,col_types = 'text')

#convert to date
et_demogr$date<-as.Date.numeric(as.numeric(et_demogr$date), origin="1900-01-01")

#reduce to relevant
et_demogr<-et_demogr[,1:8]

#fix false entry
et_demogr$date[221]<-'2022-04-01'

et_demogr$quality.of.calibration<-et_demogr$`quality of calibration`

calib_quality<-rep(NA,nrow(et_demogr))
calib_quality<-with(et_demogr,ifelse(grepl('good',quality.of.calibration),'good',calib_quality))
calib_quality<-with(et_demogr,ifelse(grepl('ok',quality.of.calibration),'good',calib_quality))
calib_quality<-with(et_demogr,ifelse(grepl('moderate',quality.of.calibration),'medium',calib_quality))
calib_quality<-with(et_demogr,ifelse(grepl('medium',quality.of.calibration),'medium',calib_quality))
calib_quality<-with(et_demogr,ifelse(grepl('bad',quality.of.calibration),'bad',calib_quality))
calib_quality<-with(et_demogr,ifelse(grepl('low',quality.of.calibration),'bad',calib_quality))
calib_quality<-with(et_demogr,ifelse(grepl('failed',quality.of.calibration),'failed',calib_quality))
calib_quality<-with(et_demogr,ifelse(grepl('no calibration',quality.of.calibration),'failed',calib_quality))
calib_quality<-with(et_demogr,ifelse(grepl('not possible',quality.of.calibration),'failed',calib_quality))
calib_quality<-with(et_demogr,ifelse(is.na(calib_quality),'else',calib_quality))

et_demogr<-data.frame(et_demogr,calib_quality)

#reorder levels
et_demogr$calib_quality<-factor(et_demogr$calib_quality,levels=c('good','medium','bad','failed','else'))

#rename variables
names(et_demogr)[2]<-"t"

#remove duplicates
table(duplicated(interaction(et_demogr$ID,et_demogr$t)))
interaction(et_demogr$ID,et_demogr$t)[duplicated(interaction(et_demogr$ID,et_demogr$t))]
##--> remove duplicated data (session data not saved / battery aborted)
delete_rows<-c(49,209,275)
et_demogr<-et_demogr[-delete_rows,]

#fix timepoint
table(et_demogr$t)
table(demogr$t)
et_demogr$t<-ifelse(et_demogr$t %in% c('baseline','Baseline','T1'),'T2',et_demogr$t)
et_demogr$t<-gsub('fu','FU',et_demogr$t)
et_demogr$t<-ifelse(grepl('K',et_demogr$ID) & et_demogr$t=='FU','FU2',et_demogr$t) 
#--> consider that controls have a later follow-up

#assessments per timepoint
with(et_demogr,table(t))

#select relevant variables and define group
et_demogr<-select(et_demogr,ID,t,date,version,comment,tester,calib_quality)
names(et_demogr)[names(et_demogr)=='version']<-'et_battery_version'
names(et_demogr)[names(et_demogr)=='date']<-'date_et'

#merge
et_demogr$ID[!et_demogr$ID %in% demogr$ID_Studie]
et_demogr<-et_demogr[!et_demogr$ID=='942_K',]
demogr$ID_Studie<-ifelse(demogr$ID_Studie=='980_k','980_K',demogr$ID_Studie)

demogr<-merge(demogr,et_demogr,by.x=c('ID_Studie','t'),by.y=c('ID','t'),all.x=T)

```

# reorder timepoint variable

```{r timepoint variable}

##reorder factor
et_demogr$t<-factor(et_demogr$t,levels=c('T2','T4','T6','FU2','FU3','FU4'))
demogr$t<-factor(demogr$t,levels=c('T1','T2','T3','T4','T5','T6','FU','FU2','FU3'))

```

# define date at timepoint

```{r date}

names(demogr)


t_date<-demogr$date_escs
t_date[is.na(t_date)]<-demogr$date_cbcl[is.na(t_date)]
t_date[is.na(t_date)]<-demogr$date_boscc[is.na(t_date)]
t_date[is.na(t_date)]<-demogr$date_iq[is.na(t_date)]
t_date[is.na(t_date)]<-demogr$date_srs[is.na(t_date)]
t_date[is.na(t_date)]<-demogr$date_rbsr[is.na(t_date)]
t_date[is.na(t_date)]<-as.character(format(demogr$date_et, "%d.%m.%Y"))[is.na(t_date)]

t_date<-as.Date(t_date,format = "%d.%m.%Y")
hist(t_date,30)
table(is.na(t_date))

demogr$t_date<-t_date

```

# define group

```{r group definition}

## define group and save to files
demogr$group <- "autistic"
demogr$group[grep("_K",demogr$ID_Studie)]<-"non autistic"

with(demogr,table(Gruppe,group))

```

# define age

```{r define age}

demogr$Geburt_Index<-as.Date(demogr$Geburt_Index)

demogr$t_age<-as.numeric(demogr$t_date - demogr$Geburt_Index)/30
hist(demogr$t_age)

```


#save to file

```{r save }

#save(demogr, et_demogr, file=paste0(savepath,'demogr_total_0324.Rdata'))
save(demogr, et_demogr, file=paste0(savepath,'demogr_total_0424.Rdata'))

```

